---
title: "LTFS"
author: "Amit Agni"
date: "13/04/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(data.table,tidyverse,lubridate,here,DataExplorer,outliers,DescTools,caret)
gc()


```

### Data load and basic cleanup
```{r}

DT_train <- fread(here::here("100_data_raw-input","train.csv"))
DT_test <- fread(here::here("100_data_raw-input","test.csv"))

DT_train$flag <- "train"
DT_test$flag <- "test"

DT_test$loan_default <- 1

DT <- rbind(DT_train,DT_test)


#to avoid date of births like 2068 instead of 1968

DT$Date.of.Birth <- dplyr::if_else(dmy(DT$Date.of.Birth) > Sys.Date(),
                            dmy(DT$Date.of.Birth) - years(100),
                            dmy(DT$Date.of.Birth))

DT$DisbursalDate <- dmy(DT$DisbursalDate)


#Some Employment types are blank
#Set them fo Self Employed (TO DO : Missing value Imputation)
DT[flag=="train",.N,by=.(Employment.Type,loan_default)]
DT[flag=="test",.N,by=.(Employment.Type,loan_default)]
DT[,Employment.Type := ifelse(Employment.Type == "","Self employed",as.character(Employment.Type))]


#drop mobile no, not useful
DT$MobileNo_Avl_Flag <- NULL

#convert into months


DT[,avg.acct.age.months := as.integer(str_extract_all(AVERAGE.ACCT.AGE,"[0-9]+",simplify = TRUE)[,1]) * 12 + as.integer(str_extract_all(AVERAGE.ACCT.AGE,"[0-9]+",simplify = TRUE)[,2])]

DT[,.(AVERAGE.ACCT.AGE,avg.acct.age.months)]


DT[,credit.history.length.months := as.integer(str_extract_all(CREDIT.HISTORY.LENGTH,"[0-9]+",simplify = TRUE)[,1]) * 12 + as.integer(str_extract_all(CREDIT.HISTORY.LENGTH,"[0-9]+",simplify = TRUE)[,2])]

DT[,.(CREDIT.HISTORY.LENGTH,credit.history.length.months)]


DT$AVERAGE.ACCT.AGE <- NULL
DT$CREDIT.HISTORY.LENGTH <- NULL


#remove ID column
DT$UniqueID <- NULL



```


Explore PRI and SEC account features (SPARSE DISTRIBUTIONS)
Convert them to factors
```{r}

unique(DT$PRI.ACTIVE.ACCTS)
unique(DT$PRI.NO.OF.ACCTS)

group_category(data = DT, feature = "PRI.NO.OF.ACCTS", threshold = 0.1,update = TRUE)
group_category(data = DT, feature = "PRI.ACTIVE.ACCTS", threshold = 0.1,update = TRUE)
group_category(data = DT, feature = "PRI.OVERDUE.ACCTS", threshold = 0.001,update = TRUE)

group_category(data = DT, feature = "SEC.NO.OF.ACCTS", threshold = 0.002,update = TRUE)
group_category(data = DT, feature = "SEC.ACTIVE.ACCTS", threshold = 0.0005,update = TRUE)
group_category(data = DT, feature = "SEC.OVERDUE.ACCTS", threshold = 0.0001,update = TRUE)

group_category(data = DT, feature = "NEW.ACCTS.IN.LAST.SIX.MONTHS", threshold = 0.002,update = TRUE)
group_category(data = DT, feature = "DELINQUENT.ACCTS.IN.LAST.SIX.MONTHS", threshold = 0.0005,update = TRUE)
group_category(data = DT, feature = "NO.OF_INQUIRIES", threshold = 0.005,update = TRUE)



```



bin amounts has huge outliers

but below 
doesnt seem to be the right approach


```{r}

summary(DT[ ,.(PRI.DISBURSED.AMOUNT,PRI.SANCTIONED.AMOUNT,PRI.CURRENT.BALANCE)])

summary(DT$PRI.SANCTIONED.AMOUNT)

length(which(DT$PRI.SANCTIONED.AMOUNT <0))
length(which(DT$PRI.DISBURSED.AMOUNT <0))
length(which(DT$PRI.CURRENT.BALANCE <0))

length(which(DT$SEC.SANCTIONED.AMOUNT <0))
length(which(DT$SEC.DISBURSED.AMOUNT <0))
length(which(DT$SEC.CURRENT.BALANCE <0))

DT$PRI.SANCTIONED.AMOUNT <- dplyr::if_else(DT$PRI.SANCTIONED.AMOUNT <= 0,0,log(DT$PRI.SANCTIONED.AMOUNT))
DT$PRI.DISBURSED.AMOUNT <- dplyr::if_else(DT$PRI.DISBURSED.AMOUNT <= 0,0,log(DT$PRI.DISBURSED.AMOUNT))
DT$PRI.CURRENT.BALANCE <- dplyr::if_else(DT$PRI.CURRENT.BALANCE <= 0,0,log(DT$PRI.CURRENT.BALANCE))


DT$SEC.SANCTIONED.AMOUNT <- dplyr::if_else(DT$SEC.SANCTIONED.AMOUNT <= 0,0,log(DT$SEC.SANCTIONED.AMOUNT))
DT$SEC.DISBURSED.AMOUNT <- dplyr::if_else(DT$SEC.DISBURSED.AMOUNT <= 0,0,log(DT$SEC.DISBURSED.AMOUNT))
DT$SEC.CURRENT.BALANCE <- dplyr::if_else(DT$SEC.CURRENT.BALANCE <= 0,0,log(DT$SEC.CURRENT.BALANCE))


ggplot(DT) +
    geom_histogram(aes(x=PRI.SANCTIONED.AMOUNT))
ggplot(DT) +
    geom_histogram(aes(x=PRI.DISBURSED.AMOUNT))
ggplot(DT) +
    geom_histogram(aes(x=PRI.CURRENT.BALANCE))

ggplot(DT) +
    geom_histogram(aes(x=SEC.SANCTIONED.AMOUNT))
ggplot(DT) +
    geom_histogram(aes(x=SEC.DISBURSED.AMOUNT))
ggplot(DT) +
    geom_histogram(aes(x=SEC.CURRENT.BALANCE))




DT$PRI.SANCTIONED.AMOUNT.quantiles <- cut(DT$PRI.SANCTIONED.AMOUNT,
                                          breaks = quantile(DT[PRI.SANCTIONED.AMOUNT >0,]$PRI.SANCTIONED.AMOUNT, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,PRI.SANCTIONED.AMOUNT.quantiles := if_else(is.na(PRI.SANCTIONED.AMOUNT.quantiles),"Q0",as.character(PRI.SANCTIONED.AMOUNT.quantiles))]
table(DT$PRI.SANCTIONED.AMOUNT.quantiles)


DT$PRI.DISBURSED.AMOUNT.quantiles <- cut(DT$PRI.DISBURSED.AMOUNT,
                                          breaks = quantile(DT[PRI.DISBURSED.AMOUNT >0,]$PRI.DISBURSED.AMOUNT, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,PRI.DISBURSED.AMOUNT.quantiles := if_else(is.na(PRI.DISBURSED.AMOUNT.quantiles),"Q0",as.character(PRI.DISBURSED.AMOUNT.quantiles))]
table(DT$PRI.DISBURSED.AMOUNT.quantiles)

DT$PRI.CURRENT.BALANCE.quantiles <- cut(DT$PRI.CURRENT.BALANCE,
                                          breaks = quantile(DT[PRI.CURRENT.BALANCE >0,]$PRI.CURRENT.BALANCE, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,PRI.CURRENT.BALANCE.quantiles := if_else(is.na(PRI.CURRENT.BALANCE.quantiles),"Q0",as.character(PRI.CURRENT.BALANCE.quantiles))]
table(DT$PRI.CURRENT.BALANCE.quantiles)



DT$SEC.SANCTIONED.AMOUNT.quantiles <- cut(DT$SEC.SANCTIONED.AMOUNT,
                                          breaks = quantile(DT[SEC.SANCTIONED.AMOUNT >0,]$SEC.SANCTIONED.AMOUNT, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,SEC.SANCTIONED.AMOUNT.quantiles := if_else(is.na(SEC.SANCTIONED.AMOUNT.quantiles),"Q0",as.character(SEC.SANCTIONED.AMOUNT.quantiles))]
table(DT$SEC.SANCTIONED.AMOUNT.quantiles)


DT$SEC.DISBURSED.AMOUNT.quantiles <- cut(DT$SEC.DISBURSED.AMOUNT,
                                          breaks = quantile(DT[SEC.DISBURSED.AMOUNT >0,]$SEC.DISBURSED.AMOUNT, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,SEC.DISBURSED.AMOUNT.quantiles := if_else(is.na(SEC.DISBURSED.AMOUNT.quantiles),"Q0",as.character(SEC.DISBURSED.AMOUNT.quantiles))]
table(DT$SEC.DISBURSED.AMOUNT.quantiles)

DT$SEC.CURRENT.BALANCE.quantiles <- cut(DT$SEC.CURRENT.BALANCE,
                                          breaks = quantile(DT[SEC.CURRENT.BALANCE >0,]$SEC.CURRENT.BALANCE, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,SEC.CURRENT.BALANCE.quantiles := if_else(is.na(SEC.CURRENT.BALANCE.quantiles),"Q0",as.character(SEC.CURRENT.BALANCE.quantiles))]
table(DT$SEC.CURRENT.BALANCE.quantiles)




DT$PRIMARY.INSTAL.AMT.quantiles <- cut(DT$PRIMARY.INSTAL.AMT,
                                          breaks = quantile(DT[PRIMARY.INSTAL.AMT >0,]$PRIMARY.INSTAL.AMT, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,PRIMARY.INSTAL.AMT.quantiles := if_else(is.na(PRIMARY.INSTAL.AMT.quantiles),"Q0",as.character(PRIMARY.INSTAL.AMT.quantiles))]
table(DT$PRIMARY.INSTAL.AMT.quantiles)

DT$SEC.INSTAL.AMT.quantiles <- cut(DT$SEC.INSTAL.AMT,
                                          breaks = quantile(DT[SEC.INSTAL.AMT >0,]$SEC.INSTAL.AMT, probs = c(0,0.25,0.5,0.75,1))
                                          ,labels = c("Q1","Q2","Q3","Q4"))
DT[,SEC.INSTAL.AMT.quantiles := if_else(is.na(SEC.INSTAL.AMT.quantiles),"Q0",as.character(SEC.INSTAL.AMT.quantiles))]
table(DT$SEC.INSTAL.AMT.quantiles)





```


Create date features
```{r}

#source :https://stackoverflow.com/questions/1995933/number-of-months-between-two-dates/1996404
DT$age.at.disbursal <- interval(DT$Date.of.Birth,DT$DisbursalDate) %/% months(1)


#option did not work
#https://stackoverflow.com/questions/10836503/convert-difftime-time-to-years-months-and-days
#DT$age.at.disbursal <- as.POSIXct(c(difftime(DT$DisbursalDate,DT$Date.of.Birth, units = "secs")),origin = DT$Date.of.Birth)

DT[,.(age.at.disbursal,avg.acct.age.months,credit.history.length.months)]

#Evertyhing in 2018 ?
DT$disbursal.year <- year(DT$DisbursalDate)
unique(DT$disbursal.year)
DT$disbursal.year <- NULL

DT$disbursal.month <- month(DT$DisbursalDate)
DT$disbursal.month <- as.factor(as.character(DT$disbursal.month))

glimpse(DT)




```


cnvert some categorical columns into numeric

```{r }
#Factor columns
str(DT[,names(which(lapply(DT, is.factor)==TRUE)),with=FALSE])



#Score description ignore
DT[,.(count = .N,
      minscore = min(PERFORM_CNS.SCORE),
      maxscore = max(PERFORM_CNS.SCORE)), by =PERFORM_CNS.SCORE.DESCRIPTION ][order(minscore)]

unique(DT$loan_default)

#Suppliers with their total loans and default pct
temp <- DT[flag=="train",.N,by=.(supplier_id,loan_default)][
    ,.(supplier_id.tot_loans = sum(N),loan_default,supplier_id.default.pct = N/sum(N)),by = supplier_id][loan_default == 1]

temp[,loan_default:=NULL]

DT <- merge(DT,temp,by="supplier_id")

glimpse(DT)

#Current pin code with their total loans and default pct
temp <- DT[flag=="train",.N,by=.(Current_pincode_ID,loan_default)][
    ,.(Current_pincode_ID.tot_loans = sum(N),loan_default,Current_pincode_ID.default.pct = N/sum(N)),by = Current_pincode_ID][loan_default == 1][order(-Current_pincode_ID.tot_loans)]

temp[,loan_default:=NULL]

DT <- merge(DT,temp,by="Current_pincode_ID")


#Current branch_id with their total loans and default pct
temp <- DT[flag=="train",.N,by=.(branch_id,loan_default)][
    ,.(branch_id.tot_loans = sum(N),loan_default,branch_id.default.pct = N/sum(N)),by = branch_id][loan_default == 1][order(-branch_id.tot_loans)]

temp[,loan_default:=NULL]

DT <- merge(DT,temp,by="branch_id")


#Current Employee_code_ID with their total loans and default pct
temp <- DT[flag=="train",.N,by=.(Employee_code_ID,loan_default)][
    ,.(Employee_code_ID.tot_loans = sum(N),loan_default,Employee_code_ID.default.pct = N/sum(N)),by = Employee_code_ID][loan_default == 1][order(-Employee_code_ID.tot_loans)]

temp[,loan_default:=NULL]

DT <- merge(DT,temp,by="Employee_code_ID")


#Current State_ID with their total loans and default pct
temp <- DT[flag=="train",.N,by=.(State_ID,loan_default)][
    ,.(State_ID.tot_loans = sum(N),loan_default,State_ID.default.pct = N/sum(N)),by = State_ID][loan_default == 1][order(-State_ID.tot_loans)]

temp[,loan_default:=NULL]

DT <- merge(DT,temp,by="State_ID")




#Drop the high factor columns
glimpse(DT)



```


convert to factors
```{r}

#characters
temp <- names(which(lapply(DT, is.character)==TRUE))
temp
DT[, (temp) := lapply(.SD, as.factor),.SDcols = temp]


#additional columns
temp <- c("manufacturer_id","Employment.Type","Aadhar_flag","PAN_flag","VoterID_flag","Driving_flag","Passport_flag","loan_default")
DT[, (temp) := lapply(.SD, as.factor),.SDcols = temp]



glimpse(DT)
str(DT)

```




Drop features
```{r}
#factor features
temp <- c("branch_id","supplier_id","Current_pincode_ID","State_ID","Employee_code_ID")

DT[,(temp) := NULL]

#date features
temp <- c("Date.of.Birth","DisbursalDate")
DT[,(temp) := NULL]


#drop PERFORM_CNS.SCORE as it captured in the description

DT$PERFORM_CNS.SCORE <- NULL





DT$PRI.SANCTIONED.AMOUNT <- NULL
DT$PRI.DISBURSED.AMOUNT <- NULL
DT$PRI.CURRENT.BALANCE <- NULL


DT$SEC.SANCTIONED.AMOUNT <- NULL
DT$SEC.DISBURSED.AMOUNT <- NULL
DT$SEC.CURRENT.BALANCE <- NULL

DT$PRIMARY.INSTAL.AMT <- NULL
DT$SEC.INSTAL.AMT <-NULL



```


Box Cox transformation of numeric columns

```{r}
temp <-names(which(lapply(DT,is.numeric)==TRUE))

preProcValues <- caret::preProcess(DT[,(temp),with = FALSE], method = "BoxCox")
DT_tran <- predict(preProcValues, DT[,(temp),with = FALSE])

glimpse(DT_tran)
plot_histogram(DT_tran)

#remove the columns from DT and cbind the transformed columns
DT[,(temp) := NULL]

DT <- cbind(DT,DT_tran)

glimpse(DT)
str(DT)

```




Data Explorer


```{r eval = FALSE}
p_load(DataExplorer)

#create_report(DT[flag == "train"], y = "loan_default")

config <- configure_report(
  add_plot_prcomp = FALSE,
  global_ggtheme = quote(theme_minimal(base_size = 14))
)

str(DT)
create_report(DT[flag == "train",-c("flag"),with = FALSE], config = config,y = "loan_default")


#plot_missing(DT_train)
#plot_bar(DT_train)
#plot_histogram(DT_train)


```



GBM using caret

```{r}

DT$loan_default <- factor(DT$loan_default,labels = c("No","Yes"))
unique(DT$loan_default)

index <- createDataPartition(y=DT[flag =="train",]$loan_default, p=0.99, list=FALSE) 

train <-DT[flag =="train"][index,]
test <-DT[flag =="train",][-index,]

train$flag <- NULL
test$flag <- NULL

table(train$loan_default)
table(test$loan_default)

str(test)
gc(reset=TRUE)

control <- trainControl(method="repeatedcv", number=3, repeats=1,classProbs = TRUE)
metric <- "Kappa"
shrinkage <- 0.01
#preproc <-  c("center", "scale")
grid <-  expand.grid(interaction.depth = c(1, 5, 9), 
                        n.trees = 1000, 
                        shrinkage = 0.01,
                        n.minobsinnode = 20)


gbmFit1 <- train(loan_default ~ ., data = test 
                 ,method = "gbm" 
                 ,trControl = control
                 ## This last option is actually one
                 ## for gbm() that passes throug
                 ,metric=metric
#                 ,tuneGrid = grid
#                ,shrinkage = 0.01    
                 ,verbose = FALSE)

gbmFit1



```



```{r}
glimpse(DT_new)

p_load(caret)
temp <- c("branch_id","supplier_id","Current_pincode_ID","Employee_code_ID","Date.of.Birth","DisbursalDate","flag", "UniqueID")


index <- createDataPartition(y=DT_new[flag =="train",]$loan_default, p=0.9, list=FALSE) 
train <-DT_new[flag =="train",!temp, with = FALSE][index,]
test <-DT_new[flag =="train",!temp, with = FALSE][-index,]

gc(reset=TRUE)
#table(train$is_attributed,as.Date(train$click_time))
#table(test$is_attributed,as.Date(test$click_time))

control <- trainControl(method="repeatedcv", number=5, repeats=3)
metric <- "Kappa"
preproc <-  c("center", "scale")

###################################################
###########   Try difference models     ###########
###################################################

glimpse(train)
fit.glm0 <- train(loan_default ~ .
                  , data=test, method="rf"
                  ,family = "binomial"
                  , trControl=control
                  # ,allowParallel = TRUE
                  # , direction = "forward"
                  , metric=metric
                  #, preProc = preproc
)
summary(fit.glm0)

table(train$app_rank)
table(train$os_rank)
table(train$channel_rank)
table(train$ip_rank)



#AIC: 1343.8

str(test)
predict.glm0<-predict.train(object=fit.glm0,
                            newdata=test,type="prob")
predict.glm0



```



Hierarchical clustering of manufacturers

```{r eval = FALSE}

which(lapply(DT_new,is.factor) == TRUE)

glimpse(DT_new[,!temp,with=FALSE])

dist <- dist(scale(DT_new[,!temp,with=FALSE]),method = "euclidean")

c <- hclust(dist,method = "complete")
plot(c)
plot(color_branches(as.dendrogram(c),h=5))
cluster_assignments <- cutree(c,h=5)
cluster_assignments


ggplot(cbind(mtcars[,1:2],cluster_assignments)) +
    geom_point(aes(x=mpg,y=cyl,
                   shape = factor(cyl),
                   color=factor(cluster_assignments))
               ,position = "jitter")

temp <- setDT(cbind(mtcars[,c(1,3,4,5,6,7)],cluster_assignments))
temp[,c(.N,lapply(.SD,mean)), by = cluster_assignments]


         


```




Correlation

```{r}
str(DT)

temp <- cor(DT_new[, lapply(DT_new, is.numeric) == TRUE, with = FALSE][,-1])

#ggcorrplot::ggcorrplot(temp, hc.order = TRUE, type = "lower")

ggcorrplot::ggcorrplot(temp,lab_size = 3,lab=TRUE,tl.cex = 10)


class(temp)
head(temp)

temp[which(temp>0.8),]


DT[]

temp <- names(which(lapply(DT_new,is.numeric)==TRUE))

prcomp(DT_new[,temp, with= FALSE])

p_load(DataExplorer)
plot_prcomp(DT_new[,temp, with= FALSE][,-72], variance_cap = 0.9, nrow = 2L, ncol = 2L)

temp
glimpse(DT_new)

```


One hot encoding
```{r eval= FALSE}
temp <- c("manufacturer_id","Employment.Type","State_ID","MobileNo_Avl_Flag","Aadhar_flag","PAN_flag","VoterID_flag","Driving_flag",
"Passport_flag","PERFORM_CNS.SCORE.DESCRIPTION")

str(DT)

encoder <- onehot(DT[,temp,with= FALSE],max_levels = 30)
temp2 <- predict(encoder, DT)



DT_new <- cbind(DT[,!temp,with = FALSE],temp2)

str(DT_new)



#mltools::one_hot(DT[,temp,with= FALSE], sparsifyNAs = TRUE, naCols = TRUE,
#  dropCols = TRUE, dropUnusedLevels = FALSE)


```



Create ratio features
```{r eval = FALSE}
str(DT)

DT$PRI.DISBURSED.AMOUNT_BY_PRI.SANCTIONED.AMOUNT <- ifelse(DT$PRI.SANCTIONED.AMOUNT == 0, 0, DT$PRI.DISBURSED.AMOUNT/DT$PRI.SANCTIONED.AMOUNT)

DT$PRI.CURRENT.BALANCE_BY_PRI.DISBURSED.AMOUNT <- ifelse(DT$PRI.DISBURSED.AMOUNT == 0 ,0 , DT$PRI.CURRENT.BALANCE/DT$PRI.DISBURSED.AMOUNT)

DT$PRI.CURRENT.BALANCE_BY_PRI.SANCTIONED.AMOUNT <- ifelse(DT$PRI.DISBURSED.AMOUNT == 0 ,0 , DT$PRI.CURRENT.BALANCE/DT$PRI.SANCTIONED.AMOUNT)


DT$SEC.DISBURSED.AMOUNT_BY_SEC.SANCTIONED.AMOUNT <- ifelse(DT$SEC.SANCTIONED.AMOUNT == 0,0, DT$SEC.DISBURSED.AMOUNT/DT$SEC.SANCTIONED.AMOUNT)

DT$SEC.CURRENT.BALANCE_BY_SEC.DISBURSED.AMOUNT <- ifelse(DT$SEC.DISBURSED.AMOUNT == 0,0,DT$SEC.CURRENT.BALANCE/DT$SEC.DISBURSED.AMOUNT)




```


Box cox visualisation
```{r eval= FALSE}

names(which(lapply(DT,is.numeric)==TRUE))


BoxCoxValues <- apply(DT[,(names(which(lapply(DT,is.numeric)==TRUE))),with=FALSE]
                      , 2, function(x) caret::BoxCoxTrans(x, na.rm = TRUE))
x = list()

for (i in 1:ncol(DT[,(names(which(lapply(DT,is.numeric)==TRUE))),with=FALSE])){
     lambda <- BoxCoxValues[[i]][[1]]
     x[[i]] <- lambda
}

lambda = do.call(rbind, x)
lambda_df <- as.data.frame(cbind(colnames(DT[,(names(which(lapply(DT,is.numeric)==TRUE))),with=FALSE]),lambda))
colnames(lambda_df)[1] <- "Column"
colnames(lambda_df)[2] <- "lambda"

setDT(lambda_df)[!is.na(lambda)]

```

